---
title: "COMPSCIX 415.2 Homework 1"
author: "Elaine Phan"
date: "6/11/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
My Github repository for my assignments can be found at this URL: [https://github.com/ElainePhan/-compscix-415-2-assignments/blob/master/README.md](https://github.com/ElainePhan/-compscix-415-2-assignments/blob/master/README.md)
and replace “https://github.com/ElainePhan/-compscix-415-2-assignments/blob/master/README.md” with your github repository URL which you can copy from your web browser.
```{r load_packages, warning=FALSE, message=FALSE}
library(mdsr)
library(tidyverse)
```



```{r}
data("WorldCities")

```
?WorldCities
Question 1 : How many observations and variables are there in this data set? What are
some of the variable names? Type up your answer in your document using complete sentences.
```{r}

glimpse(WorldCities)
```


```{r}

WorldCities <- head(WorldCities, 200) # 200 rows
country_col <- WorldCities$country
unique(country_col)
```
```{r}
reg <- WorldCities$region
unique(reg)
```


```{r}

```
View(WorldCities)

QUESTION 2: There is a column called region in the data set. Can you extract this and show
only the unique values?
```{r}
country_col <- WorldCities$region
unique(country_col)
```

```{r}
region_col <- WorldCities$region
unique(region_col)
```




```{r}
country_col <- select(WorldCities, country)
country_col <- WorldCities %>% select(country)
WorldCities %>% select(region) %>% head(5)
```

```{r}
country_col <- select(WorldCities, country)
country_col <- WorldCities %>% select(country)
WorldCities %>% select(region) %>% head(5)
```
QUESTION 3: Can you extract and show the unique entries from the country column in
WorldCities using one line of code and two %>% operators? The output will look like this:
```{r}
WorldCities %>% select(country) %>% unique()
```



Question 4
```{r}
```
```{r}
WorldCities %>% ggplot(aes(x = population)) +
geom_histogram() +
xlab('City Population')
```

```{r}
WorldCities %>% ggplot(aes(x = population)) +
geom_histogram() +
xlab('The Whole Citys Population ') +
  ylab('Count Number of Population') +
  ggtitle('Poputaion Graph') +
  theme_bw()
```
 







